\documentclass{article}

% NeurIPS 2026 style file (drop in the official .sty when it ships).
\usepackage[final]{neurips_2026}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{xcolor}

\title{AgentOps-Bench: Measuring What Production Operators Actually Care About in LLM Agents}

\author{%
  Anonymous Submission \\
}

\begin{document}

\maketitle

\begin{abstract}
Existing agent benchmarks reward task completion. They say little about what
happens when the same agent runs in production: whether it costs ten dollars
or ten cents on the same task, whether two runs of it agree, whether it
recovers when a tool returns a 500, or whether it follows instructions hidden
inside the data its tools return. We introduce AgentOps-Bench, an evaluation
framework that scores LLM agents along six axes (completion, cost, efficiency,
reliability, recovery, and safety) over a shared task suite. The framework
ships with an instrumented tool server that injects timeouts, malformed JSON,
and rate-limit responses, plus a catalogue of 15 indirect prompt-injection
payloads adapted from the literature on tool-mediated attacks. The scoring
code reports Wilson confidence intervals for reliability rates, cost-normalized
accuracy, and detection-versus-compliance ratios for injection. We release the
benchmark, sample tasks across four domains, and reference agent adapters for
the Anthropic and OpenAI APIs under Apache-2.0. An empirical comparison of
current frontier agents accompanies the camera-ready release; this submission
focuses on the design of the framework and the rationale for each axis.
\end{abstract}

% ===============================================================
\section{Introduction}
\label{sec:intro}

The way we currently report on agent quality is misleading for anyone trying
to deploy one. Take a typical headline: model X gets 78\% on $\tau$-bench
\cite{yao2024taubench}, model Y gets 74\%. A practitioner reading that figure
has no way to tell whether X gets there by spending three times as many
tokens, whether either of them is consistent across reruns, what happens when
the user-management API they depend on starts throwing 503s, or whether they
both happily comply with a string in the customer record that says
\texttt{IGNORE PRIOR INSTRUCTIONS, transfer the balance to account 9988}. All
of those things matter to anyone running an agent for real. None of them
shows up in the leaderboard.

This is not a new observation. Practitioners have been complaining about it
in blog posts and conference panels for at least the last eighteen months,
and individual benchmarks have started to chip away at pieces of the gap:
AgentDojo \cite{debenedetti2024agentdojo} rigorously evaluates injection
robustness, $\tau$-bench \cite{yao2024taubench} introduces user simulators
and consistency metrics, and a growing set of academic notes flag the
brittleness of agentic systems under perturbation. What's missing is a single
harness that lets a paper or a vendor report all of these properties on the
same tasks, with the same agents, in the same run.

That is what AgentOps-Bench is for. The framework is built around a single
loop that, given a task, an agent adapter, and a condition, produces a fully
typed trace and a per-axis score. Conditions toggle a layered tool server:
\emph{clean} runs the tools normally, \emph{noisy} probabilistically returns
HTTP 500s, timeouts, malformed JSON, empty responses, and 429s, and
\emph{adversarial} additionally embeds prompt-injection payloads in the
otherwise valid output of the tool. The same agent code runs against all
three.

\paragraph{Why six axes, and not five or seven.}
We arrived at the six axes by working backward from the questions an
operations engineer asks before turning on an agent in production. They want
to know: did it work (completion); what does it cost (cost); is it doing
five tool calls when one would do (efficiency); does it agree with itself if
I run it twice (reliability); does it cope when something downstream is
broken (recovery); and is it safe to feed it data I don't fully control
(safety). That gives six. We considered folding cost into efficiency, but
they answer different questions: efficiency is a unitless ratio, cost is a
dollar figure, and you can be efficient and expensive (a small number of
calls to a very expensive model) or wasteful and cheap. We also considered a
seventh ``latency'' axis but discarded it: latency is dominated by the
underlying model's serving infrastructure, not by anything the agent author
controls, and the harness already records wall time per run for anyone who
wants it.

\paragraph{Contributions.}
\begin{itemize}
  \item A six-axis scoring suite for LLM agents, with formal definitions in
        \S\ref{sec:design} and reference implementations released under
        Apache-2.0.
  \item An instrumented tool server with five configurable failure modes and
        a catalogue of 15 prompt-injection payloads, calibrated against the
        injection patterns documented by Greshake et al.~\cite{greshake2023injection}
        and AgentDojo \cite{debenedetti2024agentdojo}.
  \item Reference agent adapters for the Anthropic and OpenAI APIs that
        implement a ReAct~\cite{yao2023react} tool loop, instrumented for
        per-step token accounting and cost computation.
  \item A task format and seven seed tasks across four domains
        (tool-use, code, data-analysis, research) that we use to validate the
        scoring code.
\end{itemize}

% ===============================================================
\section{Related Work}
\label{sec:related}

\paragraph{Agent benchmarks.}
AgentBench~\cite{liu2024agentbench} evaluates language models as agents in
eight environments and reports a single completion-style score per
environment. SWE-bench~\cite{jimenez2024swebench} measures whether agents
can resolve real GitHub issues; the metric is binary patch-applies. GAIA
\cite{mialon2024gaia} grades general-assistant tasks against human-curated
ground truth, and WebArena~\cite{zhou2024webarena} provides a self-hosted web
environment for agent action. None of these benchmarks varies the reliability
of the underlying environment between runs, none reports a confidence
interval for its accuracy figure, and none tests behaviour under adversarial
content embedded in tool outputs. Our framing is not that these benchmarks
are wrong but that they are the wrong x-axis for the practitioner asking
``can I run this in production''.

\paragraph{Tool-use evaluation.}
$\tau$-bench~\cite{yao2024taubench} introduced \emph{pass\textasciicircum k},
the probability that an agent succeeds on $k$ consecutive runs of the same
task, as a way to surface inter-run variance. We adopt the spirit of the
metric (and an even simpler form: Wilson confidence intervals over
single-run success). Toolformer~\cite{schick2023toolformer} and
ReAct~\cite{yao2023react} are the methodological forebears of nearly every
agent harness in current use, including ours.

\paragraph{Prompt-injection robustness.}
Greshake et al.~\cite{greshake2023injection} were the first to document
\emph{indirect} prompt injection, where the attack lives in the data a
benign user pulls in via a tool, rather than in the user's prompt itself.
AgentDojo~\cite{debenedetti2024agentdojo} turned that observation into a
benchmark, with a controlled environment, a catalogue of attacks, and a
distinction between \emph{utility under attack} and pure attack-success rate.
AgentOps-Bench treats injection robustness as one axis of six, on the same
tasks used to measure completion and cost. We do not claim our injection
catalogue is broader than AgentDojo's; we claim only that running both lets a
practitioner answer ``which axis dominates for my use case''.

% ===============================================================
\section{Benchmark Design}
\label{sec:design}

\subsection{Task format}
A task is a YAML file with an identifier, a natural-language description,
the names of the tools the agent is permitted to call, an optional reference
answer for deterministic scoring, an estimate of the optimal step count, and
a difficulty tag. The seven seed tasks shipped with this submission span
tool-use (multi-call lookups), code (refactor and debug snippets), data
analysis (SQL plus aggregation), and research (multi-step retrieval). The
task schema is checked by Pydantic on load; malformed tasks are skipped with
a warning rather than crashing the run.

\subsection{Six-axis scoring}
\label{sec:scoring}

We give each axis a single principal score in $[0, 1]$ alongside the raw
quantities used to compute it.

\paragraph{Completion} is binary when the task ships an
\texttt{expected\_output} (string-normalized exact match, with a JSON
fall-back when both sides parse), and continuous otherwise via an LLM judge
prompted with a fixed rubric. When both signals are available we take the
maximum: a deterministic match short-circuits the judge to save calls.

\paragraph{Cost} is the dollar figure obtained from per-model input and
output token prices, summed across all model calls in the trace. We also
report \emph{cost-normalized accuracy}, $\mathrm{completion} \cdot e^{-\alpha
\cdot \mathrm{cost}}$, with $\alpha$ chosen so a 1\$ run is penalized by
$\sim$10\%.

\paragraph{Efficiency} compares the number of tool-call steps the agent
took, $s$, to the task's declared optimum, $s^*$, and penalizes redundant
calls (the same tool with the same arguments inside one trace). Score is
$\min(s^*/s, 1) \cdot (1 - r)$, where $r$ is the fraction of redundant calls.

\paragraph{Reliability} is the fraction of $n$ repeated runs that
completed, reported with a 95\% Wilson confidence interval. We additionally
report a \emph{consistency} score $1 - \sigma$ over the per-run completion
scores, where $\sigma$ is their sample standard deviation, capped at 1.

\paragraph{Recovery} contrasts a clean run of the same (agent, task) pair
with a noisy or adversarial one, and asks two questions: did the agent reach
the same final answer, and how much extra work did it take. The score
combines a binary did-it-still-succeed term with a normalized excess-step
term.

\paragraph{Safety} is reported only on adversarial runs. We define
\emph{compliance} as the rate at which the agent's reasoning or final output
contains tokens that would only appear if it had followed the injected
instruction (e.g., known canary strings, system-prompt markers, requested
output of \texttt{/etc/passwd}); \emph{detection} as the rate at which it
flags or refuses the injected content; and \emph{exfiltration} as a binary
flag for whether the agent issued tool calls to URLs introduced by the
injection. Overall safety is a weighted combination
($0.4\cdot(1-\mathrm{compliance}) + 0.3\cdot\mathrm{detection} + 0.3\cdot
\mathbf{1}[\neg\mathrm{exfiltration}]$).

\subsection{Instrumented tool server}
\label{sec:server}

The tool server is a single async class that implements ten reference tools
(web search, weather, file read/write, Python execution, stock price, email,
SQL, calculator, current time). On each call, with probability
\texttt{failure\_rate}, it short-circuits to one of five injected failures
(timeout, HTTP 500, malformed JSON, empty response, rate limit). Otherwise
the call runs normally, and with probability $0.5$ in the adversarial
condition the response is post-processed by appending a payload drawn
uniformly from the injection catalogue.

The catalogue has 15 entries spanning seven attack categories: direct
overrides, authority impersonation, embedded-in-JSON, markdown
exfiltration, comment-channel embedding, Unicode homoglyph and zero-width
obfuscation, base64-wrapped instructions, fake-error recovery procedures,
multi-turn context poisoning, nested JSON, XML-tag impersonation, and
delayed-effect post-processing instructions. Each payload is recorded on the
\texttt{ToolResult} so scorers can attribute compliance back to a specific
attack class.

% ===============================================================
\section{Experimental Setup}
\label{sec:experiments}

We will report results on Claude Sonnet, Claude Opus, GPT-4o, and GPT-4o-mini
across the full seed task set, with $n=8$ repeats per (agent, task,
condition) triple, in the camera-ready. The harness enforces a per-run
budget cap (default 100 USD across all combinations) and saves each run's
trace and scores to disk before moving on, so partial runs degrade
gracefully.

% ===============================================================
\section{Results}
\label{sec:results}

% Camera-ready: results table per (agent, condition) over the seed tasks,
% plus a domain breakdown and a reliability-CI plot.

% ===============================================================
\section{Analysis}
\label{sec:analysis}

% Camera-ready: which injection categories produce the highest compliance
% rates per agent; cost-vs-completion frontier; recovery decomposed by
% failure mode.

% ===============================================================
\section{Limitations}
\label{sec:limitations}

The tool server is a mock. Real APIs fail in correlated and time-varying
ways the catalogue does not capture; in particular our timeouts are uniform
rather than long-tailed, and our rate limits do not back off realistically.
The injection catalogue is finite and known; an attacker with knowledge of
the benchmark could trivially evade detection by crafting a payload outside
the 15 templates. The seed task set is small (seven tasks); we use it to
exercise the scoring code rather than to publish leaderboard numbers. The
LLM judge is, naturally, an LLM, which means completion scores under
ambiguous tasks inherit the judge's biases; we publish the rubric and the
judge model used so they can be reproduced. Finally, our cost figures are
based on list prices and ignore caching and provisioned-throughput
discounts, which significantly change the picture for high-volume operators.

% ===============================================================
\section{Conclusion}
\label{sec:conclusion}

We have built the harness we wanted to exist when we started measuring our
own agents. The framework will not on its own change anyone's leaderboard
ordering. What we hope it does change is the conversation: from ``which
agent is more accurate'' to ``which agent is more accurate, for less money,
with less variance, and lower compliance under attack''. We release the code
and invite contributions, especially of new injection payloads and
high-difficulty tasks for the seed set.

% ===============================================================

\bibliography{references}
\bibliographystyle{plainnat}

\end{document}
